Inferring the effective start dates of non-pharmaceutical interventions during \covid outbreaks

### 2021-02-06 ms/ms.tex
autocorrelation change for fixed tau model

The posterior distribution of the model parameters $P(\theta \mid \vec{X})$ is estimated using the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC)~\citep{Goodman2010}, implemented in the \texttt{emcee} Python package~\citep{Foreman-Mackey2013}.
We use the default configuration with the stretch move and a stretch scale parameter $a=2$.
For the main analysis we use 50 chains (or walkers) per region, with 7M samples per chain (no thinning was applied; 6.8M for Wuhan).
The \emph{integrated autocorrelation time} (IAT)~\citep{Foreman-Mackey2013,Goodman2010} was averaged across parameters and chains for each region. 
The average IAT was between 31.9K for Wuhan and 187K for Germany~(\autoref{fig:autocorr}).
We examined the trace plots for $\tau$ in all regions (\autoref{fig:trace}).
All chains seem to converge to the stationary distribution, in most cases before 2M samples. Thus, we discarded the first 2M samples as burn-in samples.
The only exception is Spain, in which a single chain converged at around 6M samples.
We considered this chain as part of the burn-in and removed it from the analysis.
Therefore, 50 chains with 5M samples and IAT between 32K and 187K give an effective sample size between 1,336 and 7,523.
We ran additional chains with 2M samples and a different initialization (i.e. seed). The estimated posterior distributions of $\tau$ were very similar to our main analysis, further increasing our confidence in the convergence of our inference.
For the models with fixed~$\tau$ and without~$\tau$, in some countries, we use less than 7M samples per chain because the IAT converged sooner.
In these cases the effective sample size was at between 2,454 (UK) and 10,954 (Spain) in the fixed~$\tau$ model and between 6,230 (Norway) and 94,339 (Italy) in the model without~$\tau$.

>>>>

The posterior distribution of the model parameters $P(\theta \mid \vec{X})$ is estimated using the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC)~\citep{Goodman2010}, implemented in the \texttt{emcee} Python package~\citep{Foreman-Mackey2013}.
We use the default configuration with the stretch move and a stretch scale parameter $a=2$.
For the main analysis we use 50 chains (or walkers) per region, with 7M samples per chain (no thinning was applied; 6.8M for Wuhan).
The \emph{integrated autocorrelation time} (IAT)~\citep{Foreman-Mackey2013,Goodman2010} was averaged across parameters and chains for each region. 
The average IAT was between 31.9K for Wuhan and 187K for Germany~(\autoref{fig:autocorr}).
We examined the trace plots for $\tau$ in all regions (\autoref{fig:trace}).
All chains seem to converge to the stationary distribution, in most cases before 2M samples. Thus, we discarded the first 2M samples as burn-in samples.
The only exception is Spain, in which a single chain converged at around 6M samples.
We considered this chain as part of the burn-in and removed it from the analysis.
Therefore, 50 chains with 5M samples and IAT between 32K and 187K give an effective sample size between 1,336 and 7,523.
We ran additional chains with 2M samples and a different initialization (i.e. seed). The estimated posterior distributions of $\tau$ were very similar to our main analysis, further increasing our confidence in the convergence of our inference.
For the models with fixed~$\tau$ and without~$\tau$, in some countries, we use less than 7M samples per chain because the IAT converged sooner.
In these cases the effective sample size was at between 1,451 (Germany) and 7,443 (Wuhan) in the fixed~$\tau$ model and between 6,230 (Norway) and 94,339 (Italy) in the model without~$\tau$.
